\begin{biblio}

\bibitem{svenska_19}
Jones, C. An introduction to model predictive control / University Lecture at ecole Polytechnique Federale de Lausanne, 2014.

\bibitem{Jalali}
Jalali, M. Model predictive control of vehicle stability using coordinated active steering and diferential brakes. / M. Jalali, S. Khosravani, A. Khajepour, // Mechatronics, 2017

\bibitem{Khajepour}
Jie, J. Path planning and tracking for vehicle collision avoidance based on model predictive control with multiconstraints. / J. Jie, A. Khajepour, W. W Melek // IEEE Transactions on Vehicular Technology, 2017, 66(2): 952--964

\bibitem{Visioli}
Visioli, A. Research Trends for PID Controllers. / Visioli A. // Acta Polytechnica, 2012 Vol. 52 No. 5

\bibitem{Olsson}
Ollson, C. Model Complexity and Coupling of Longitudinal and Lateral Control in Autonomous Vehicles Using Model Predictive Control / C. Ollson // KTH School of Electrical Engineering Stockholm, 2015

\bibitem{Palmqvist}
Palmqvist, M. I. Model Predictive Control for Autonomous Driving of a Truck / M. I. Palmqvist // KTH School of Electrical Engineering Stockholm, 2016

\bibitem{Dominguez}
Dominguez, S. Comparison of lateral controllers for autonomous vehicle : experimental results / S. Dominguez, A. Ali, G. Garcia, P. Martinet // 2016 IEEE 19th International Conference on Intelligent Transportation Systems, 2016

\bibitem{Polack}
Polack, P. Finite Time Stabilization of Longitudinal Control for Autonomous Vehicles via a Model-Free Approach / P. Polack, B. d'Andrea-Novel, M. Fliess, A. de La Fortella, L. Menhour // IFAC-PapersOnLine, 2017. Vol. 50, Issue 1 P. 12533-12538

\bibitem{Mayne}
Mayne, D.Q. Constrained model predictive control: Stability and optimality / D.Q. Mayne // Automatica, --- 2000.--- Vol. 36, no. 6. ---P. 789-814.

\bibitem{Gruene}
Gruene, L. Nonlinear model predictive control / L. Gruene, J. Pannek //--- Springer London, 2011.

\bibitem{Andersson}
Andersson,  J.,   Dynamic optimization with CasADi / J. Andersson,  Akesson J., M. Diehl // Decision and Control(CDC), 2012 IEEE 51st Annual Conference on. ---IEEE, 2012. ---P. 681-686.

\bibitem{wiki_tesla}
Tesla Model 3 [Электронный источник] / Wikipedia, the free encyclopedia. - Режим доступа: www.en.wikipedia.org/wiki/Tesla Model 3. - Дата доступа: 09.12.2019

\bibitem{official_tesla}
Model 3 | Tesla [Электронный источник] / Electric Cars, Solar Panels Clean Energy Storage | Tesla. - Режим доступа: www.tesla.com/model3. - Дата доступа: 09.12.2019

\bibitem{dyno_tesla}
Tesla Performance Model 3 Dyno Testing At Various SOC | Mountain Pass Performance [Электронный источник] / Mountain Pass Performance. - Режим доступа: www.mountainpassperformance.com/tesla-performance-model-3-dyno-testing-at-various-soc/. - Дата доступа: 09.12.2019

\end{biblio} 